The association of smoking status with SARS-CoV-2 infection, hospitalisation and mortality from COVID-19: A living rapid evidence review with Bayesian meta-analyses (`r paste(current_version)`)

### 2021-08-13 reports/manuscript.Rmd
v12

##    Data availability
All data contributing to the current and future review versions are available [here](https://doi.org/10.6084/m9.figshare.12756020)

All code required to reproduce the current and future analyses are available [here](https://doi.org/10.5281/zenodo.4002046)

>>>>

##    Data availability
All data contributing to the current and future review versions are available [here](https://doi.org/10.6084/m9.figshare.12756020.v7)

All code required to reproduce the current and future analyses are available [here](https://doi.org/10.5281/zenodo.5189278)
